---
title: "Introduction to sensortowerR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to sensortowerR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

An R package for interfacing with the Sensor Tower API to fetch mobile app analytics data, including app info, publisher details, revenue/download estimates, and active user metrics.

## Authentication (Important!)

This package requires a Sensor Tower API authentication token to function. **It is strongly recommended to store your token securely as an environment variable rather than hardcoding it in your scripts.**

The functions in this package will automatically look for an environment variable named `SENSORTOWER_AUTH_TOKEN`.

## Core Functions

The package provides the following main functions:

- `st_app_info()`: Search for apps or publishers and retrieve basic information (like unified IDs).
- `st_publisher_apps()`: Fetch metadata for all apps associated with a specific publisher ID.
- `st_metrics()`: Fetch detailed daily metrics (revenue, downloads, active users) for a specific unified app ID over a date range.
- `st_top_sales()`: Retrieve ranked lists of top apps based on revenue or downloads ("units") for specific criteria (OS, category, region, time period, etc.).
- `st_top_active_users()`: Retrieve ranked lists of top apps based on DAU, WAU, or MAU for specific criteria (OS, category, region, time period, etc.).

## Example Usage

Make sure you have set the `SENSORTOWER_AUTH_TOKEN` environment variable and restarted R before running these examples.

```{r, eval=FALSE}
library(sensortowerR)
library(lubridate) # For easy date creation

# --- Example 1: Get App Info ---
# Search for apps matching "Clash Royale"
app_info <- st_app_info(term = "Clash Royale", limit = 1)
print(app_info)
# Use the unified_app_id from app_info in other functions if needed

# --- Example 2: Get Publisher's Apps ---
# Fetch apps published by Supercell (replace with a valid ID)
publisher_apps <- st_publisher_apps(publisher_id = "560c48b48ac350643900b82d")
print(publisher_apps)

# --- Example 3: Fetch Detailed Metrics for One App ---
# Fetch metrics for a specific app ID (replace with a valid ID)
# Requires a valid unified_app_id known beforehand
metrics <- st_metrics(
  unified_app_id = "YOUR_VALID_UNIFIED_APP_ID",
  start_date = Sys.Date() - 15,
  end_date = Sys.Date() - 1
)
print(metrics)
head(metrics)

# --- Example 4: Get Top Apps by Downloads ---
# Get top 5 iOS Games by downloads ("units") in the US for the last full month
top_downloads <- st_top_sales(
  os = "ios",
  comparison_attribute = "absolute", # Or "delta", "transformed_delta"
  time_range = "month",
  measure = "units",
  date = floor_date(Sys.Date() - months(1), "month"), # Start of last month
  category = 6000, # iOS Games category ID
  regions = "US",  # Region is required
  limit = 5
  # device_type defaults to "total" for iOS
)
print(top_downloads)

# --- Example 5: Get Top Apps by Active Users ---
# Get top 3 Android apps by MAU worldwide for the last quarter
top_mau <- st_top_active_users(
  os = "android",
  comparison_attribute = "absolute",
  time_range = "quarter",
  measure = "MAU",
  date = floor_date(Sys.Date() - months(3), "quarter"), # Start of last quarter
  regions = "WW", # Worldwide region is required
  # category = NULL, # Optional: omit for all categories
  limit = 3
)
print(top_mau)
``` 